Wigglyhedra

### 2024-10-09 draft/wigglyhedra.tex
minor
minor corrections
expose Berlin

\begin{theorem*}
The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \defn{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
\begin{itemize}
\item the intersection of the halfspaces~$\set{\b{x} \in \HH}{\dotprod{\b{g}(\alpha)}{\b{x}} \le \kappa(\alpha)}$ for all internal wiggly arcs~$\alpha$,
\item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
\end{itemize}
\end{theorem*}

@@

	\setlength\arraycolsep{1.1pt}

@@

@@

@@

\begin{theorem}
\label{thm:wigglyhedron}
The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \defn{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
\begin{itemize}
\item the intersection of the halfspaces~$\set{\b{x} \in \HH}{\dotprod{\b{g}(\alpha)}{\b{x}} \le \kappa(\alpha)}$ for all internal wiggly arcs~$\alpha$,
\item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
\end{itemize}
\end{theorem}

@@

Recall that the $\delta$-Cambrian lattice can be realized by the $\delta$-Cambrian fan~\cite{ReadingSpeyer} and the $\delta$-associahedron of~\cite{HohlwegLange}.
Namely, to each diagonal~$(i,j)$ of the $\delta$-gon, we associate the subset~$X(\delta)$ of points of the $\delta$-gon distinct from~$0$ and~$n+1$, and located below the line~$(i,j)$, including~$i$ if and only if~$\delta_i = {+}$ and~$j$ if and only if~$\delta_j = {+}$.
The \defn{$\delta$-Cambrian fan} is the fan with a ray~$\b{g}(d) \eqdef \pi(\one_{X(d)})$ for each internal diagonal~$d$ of the $\delta$-gon and a cone~$\R_{\ge0} \setangle{\b{g}(d)}{d \in D^\circ}$ for each dissection~$D$ of the $\delta$-gon.
The \defn{$\delta$-associahedron}~$\Asso_\delta$ is the polytope defined by the equality~$\dotprod{\one_n}{\b{x}} = \binom{n+1}{2}$ and the inequalities~$\dotprod{\b{g}(d)}{\b{x}} \le \binom{|X(d)|+1}{2}$ for all internal diagonals~$d$ of the $\delta$-gon.

>>>>

\begin{theorem*}
The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \defn{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
\begin{itemize}
\item the intersection of the halfspaces~$\set{\b{x} \!\in\! \HH_{2n}\!}{\!\dotprod{\b{g}(\alpha)}{\b{x}} \!\le\! \kappa(\alpha)}$ for all internal wiggly arcs~$\alpha$,
\item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
\end{itemize}
\end{theorem*}

@@

@@

	\quad &

@@

	\quad

@@

\begin{theorem}
\label{thm:wigglyhedron}
The wiggly fan~$\wigglyFan_n$ is the normal fan of a simplicial $(2n-1)$-dimensional polytope, called the \defn{wigglyhedron}~$\wigglyhedron_n$, and defined equivalently~as
\begin{itemize}
\item the intersection of the halfspaces~$\set{\b{x} \!\in\! \HH_{2n}\!}{\!\dotprod{\b{g}(\alpha)}{\b{x}} \! \le \! \kappa(\alpha)}$ for all internal wiggly~arcs~$\alpha$,
\item the convex hull of the points~$\b{p}(T) \eqdef \sum\limits_{\alpha \in T} \kappa(\alpha) \, \b{c}(\alpha, T)$ for all wiggly pseudotriangulations~$T$.
\end{itemize}
\end{theorem}

@@

Recall that the $\delta$-Cambrian lattice can be realized by the $\delta$-Cambrian fan~\cite{ReadingSpeyer} and the $\delta$-associahedron of~\cite{HohlwegLange}.
Namely, to each diagonal~$(i,j)$ of the $\delta$-gon, we associate the subset~$X(\delta)$ of points of the $\delta$-gon distinct from~$0$ and~$n+1$, and located below the line~$(i,j)$, including~$i$ if and only if~$\delta_i = {+}$ and~$j$ if and only if~$\delta_j = {+}$.
The \defn{$\delta$-Cambrian fan} is the fan with a ray~$\b{g}(d) \eqdef \pi(\one_{X(d)})$ for each internal diagonal~$d$ of the $\delta$-gon and a cone~$\R_{\ge0} \setangle{\b{g}(d)}{d \in D^\circ}$ for each dissection~$D$ of the $\delta$-gon.
The \defn{$\delta$-associahedron}~$\Asso_\delta$ is the polytope defined by the equality~$\dotprod{\one_n}{\b{x}} = \binom{n+1}{2}$ and the inequalities~$\dotprod{\b{g}(d)}{\b{x}} \ge \binom{|X(d)|+1}{2}$ for all internal diagonals~$d$ of the $\delta$-gon.
